\huge Opto-fMRI of Monoaminergic Systems and Psychotropic Drugs

### 2017-01-05 exampleandimage/egbeamersnw.tex
Add files via upload

\documentclass{beamer}
\usepackage{chemformula}
\usepackage[utf8]{inputenc}
\usepackage[german, english]{babel} % required for rendering German special characters
\usepackage{siunitx} %pretty measurement unit rendering
\usepackage{hyperref} %enable hyperlink for urls
\usepackage{ragged2e}
\usepackage[font=scriptsize,justification=justified]{caption}
\usepackage{array,booktabs,tabularx}
\usepackage[backend=biber,bibstyle=gb7714-2015-m,%nature,%
citestyle=gb7714-2015,%,backref=true%gb，gbt7714_2005_n，
align=gb7714-2015%
]{biblatex}%biber，caspervector
\renewcommand{\bibfont}{\footnotesize}
\addbibresource[location=local]{bib.bib}

>>>>

%\let\itemudf=\item
\documentclass{beamer}
\usepackage{chemformula}
\usepackage[utf8]{inputenc}
\usepackage[german, english]{babel} % required for rendering German special characters
\usepackage{siunitx} %pretty measurement unit rendering
\usepackage{hyperref} %enable hyperlink for urls
\usepackage{ragged2e}
\usepackage[font=scriptsize,justification=justified]{caption}
\usepackage{array,booktabs,tabularx}
\usepackage[backend=biber,bibstyle=gb7714-2015-m,%nature,%
citestyle=gb7714-2015,%,backref=true%gb，gbt7714_2005_n，
align=left%
]{biblatex}%biber，caspervector
\renewcommand{\bibfont}{\footnotesize}
\addbibresource[location=local]{bib.bib}
\defbeamertemplate*{bibliography item}{numeric}
{\hbox{[\printfield{labelnumber}]}}
\setbeamertemplate{bibliography item}[numeric]%book,numeric

### 2017-01-05 exampleandimage/egpostersnr.tex
Add files via upload

\documentclass{beamer}
\usepackage[orientation=portrait,size=a0,scale=1.4,debug]{beamerposter}
\mode<presentation>{\usetheme{ZH}}
\usepackage{chemformula}
\usepackage[utf8]{inputenc}
\usepackage[german, english]{babel} % required for rendering German special characters
\usepackage{siunitx} %pretty measurement unit rendering
\usepackage{hyperref} %enable hyperlink for urls
\usepackage{ragged2e}
\usepackage[font=scriptsize,justification=justified]{caption}
\usepackage{array,booktabs,tabularx}
\usepackage[backend=biber,bibstyle=gb7714-2015-m,%nature,%
citestyle=gb7714-2015,%,backref=true%gb，gbt7714_2005_n，
align=gb7714-2015%
]{biblatex}%biber，caspervector
\renewcommand{\bibfont}{\footnotesize}
\addbibresource[location=local]{bib.bib}

@@

					\begin{myblock}{References}

@@

>>>>

\documentclass{beamer}
\usepackage[orientation=portrait,size=a0,scale=1.4,debug]{beamerposter}
\mode<presentation>{\usetheme{ZHM}}
\usepackage{chemformula}
\usepackage[utf8]{inputenc}
\usepackage[german, english]{babel} % required for rendering German special characters
\usepackage{siunitx} %pretty measurement unit rendering
\usepackage{hyperref} %enable hyperlink for urls
\usepackage{ragged2e}
\usepackage[font=scriptsize,justification=justified]{caption}
\usepackage{array,booktabs,tabularx}
\usepackage[backend=biber,bibstyle=gb7714-2015-m,%nature,%
citestyle=gb7714-2015,%,backref=true%gb，gbt7714_2005_n，
align=right%
]{biblatex}%biber，caspervector
\renewcommand{\bibfont}{\footnotesize}
\addbibresource[location=local]{bib.bib}
%\defbeamertemplate*{bibliography item}{numeric}
%{\hbox{[\printfield{labelnumber}]}}
\setbeamertemplate{bibliography item}[default]%book,numeric

@@

					\begin{block}{References}%myblock

@@

					\end{block}\vfill
